Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-05-24 doc/JFLA2022/Slides/Slides.tex
update JFLA Slides
work on JFLA slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{frame}
  \tableofcontents
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{\community}
    \begin{block}{}
      \community is an informal organization that aims to maintain interesting open source \coq projects and facilitate collaboration among Coq users on documentation, tooling, etc.
      \begin{itemize}
      \item Created in 2018,  run by volunteer Coq users on GitHub
      \item At present, over than 50 projects, maintained by over than 30 volunteers
      \item Some packages were unmaintained before their integration to \community. According to their scientific or historical interest, we decided to revive them.
        \item After their transfer, packages may be the object of large changes  and refactorings.
      \end{itemize}
    \end{block}
  \end{frame}

@@

\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=mathcomp, node distance=7.7cm] (equations) { Equations };
\end{scope}

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);
\draw[dotted, ->] (prooftheory) -- (goedel);
\draw[dotted, ->] (algo) -- (additions);
\draw[->, red] (alectryon) -- (book) ;
\draw[->, red] (chains) -- (book) ;
\draw[->, red] (gaiahydras) -- (book) ;
\draw[->, red] (hydras.south) -- (book) ;

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to provide  a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}

@@

    \item Formalization by Minki Cho, using a different representation.
{\color{darkorange}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

\begin{frame}
  \begin{block}{}
    \begin{itemize}
      \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item More examples and exercises
    \item etc.
    \end{itemize}
  \end{block}
\end{frame}

  \begin{frame}
\frametitle{Call to contributors}
  \begin{block}{}
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please contribute, reuse!}
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)

@@

\begin{frame}
  \frametitle{Ordinals in \coq}

  \begin{block}{}
    Ordinals less than {\color{mathcolor}$\omega^\omega, \epsilon_0,  \Gamma_0$} are represented as \emph{ordinal notations}: comparison, canonical sequences, partition limit/successors/zero ordinals are implemented by certified functions, allowing the user to write proofs by computation.

    \begin{footnotesize}
      \inputsnippets{./ONDef}

      \inputsnippets{../E0_Ex42}
    \end{footnotesize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% \begin{frame}
%   \tableofcontents
% \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
    \frametitle{\community}
    \begin{block}{}
      \community is an informal organization that aims to maintain interesting open source \coq projects and facilitate collaboration among Coq users on documentation, tooling, etc.
      \begin{itemize}
      \item Created in 2018,  run by volunteer Coq users on GitHub
      \item At present, over than 50 projects, maintained by over than 30 volunteers
      \item Some packages were unmaintained before their integration to \community. According to their scientific or historical interest, we decided to revive them.
        \item After their transfer, packages may be the object of large changes  and refactorings.
      \end{itemize}
    \end{block}
  \end{frame}

@@

  \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=mathcomp, node distance=7.7cm] (equations) { Equations };

   \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=equations, node distance=3cm] (libhyps) { LibHyps };
\end{scope}

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (libhyps) -- (hydras) ;

\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);
\draw[dotted, ->] (prooftheory) -- (goedel);
\draw[dotted, ->] (algo) -- (additions);
\draw[->, red] (alectryon) -- (book) ;
\draw[->, red] (chains) -- (book) ;
\draw[->, red] (gaiahydras) -- (book) ;
\draw[->, red] (hydras.south) -- (book) ;

@@

\begin{frame}
  \frametitle{Conclusion and perspectives}
  \begin{block}{}
    \begin{itemize}
    \item \Hydras wants to provide  a connection between scientific litterature and proof assistant technology:
      \begin{itemize}
      \item For the mathematician, it gives a concrete view of the mathematical contents: full proofs, examples, computable functions whenever possible, etc.
        \item  For the \coq learner, it provides a consistent set of examples,
          allowing to present and compare various formalization and proving techniques.
          \item It allows the development team to experiment various techniques of CI/CD and project organization and maintenance.
      \end{itemize}
    \end{itemize}
  \end{block}
  \end{frame}

@@

    \item Formalization by Minki Cho, using a different representation.
{\color{blue}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

\begin{frame}
  \begin{block}{}
    \begin{itemize}
      \item More results about hyper-complexity and fast growing functions
    \item New toolchain for \alectr
    \item More proof and specification patterns
    \item More examples and exercises
    \item etc.
    \end{itemize}
  \end{block}

  \begin{block}{}
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please contribute, reuse!}
      \begin{itemize}
      \item New chapters
      \item Any correction or suggestion of improvement (text and/or proofs)

@@
